Results

### 2023-04-05 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected figure caption

```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block. Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block. The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05. $N=120$". Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license., fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
```

>>>>

```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block. Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block. The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05. $N=120$. Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
```
